---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# xdgbasedir

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/xdgbasedir)](https://CRAN.R-project.org/package=xdgbasedir)
[![R-CMD-check](https://github.com/briandconnelly/xdgbasedir/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/briandconnelly/xdgbasedir/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/briandconnelly/xdgbasedir/branch/main/graph/badge.svg)](https://app.codecov.io/gh/briandconnelly/xdgbasedir?branch=main)
<!-- badges: end -->

xdgbasedir is R package that allows you to easily and consistently work with paths that comply with the [XDG Base Directory Specification](https://specifications.freedesktop.org/basedir-spec/basedir-spec-latest.html).

## Installation

You can install the development version of xdgbasedir like so:

``` r
# install.packages("remotes")
remotes::install_github("briandconnelly/xdgbasedir")
```

## Example

Let's say we wanted to read our RStudio Desktop preferences file, `rstudio-prefs.json`.
Since RStudio [complies](https://docs.posit.co/ide/desktop-pro/settings/settings.html) with the XDG Base Directory Specification, we can easily find that file no matter how the user has configured their environment.

```{r load rstudio-prefs.json}
library(xdgbasedir)

prefs_file <- path_xdg_config_home("rstudio-prefs.json")
prefs_file
```
